3D Magnetic modelling of ellipsoidal bodies

### 2017-03-15 manuscript/manuscript.tex
define the V matrix for prolate ellipsoids equal to that used for triaxial ellipsoids

For triaxial ellipsoids (i.e., $a > b > c$), these unit vectors are 
given by \citep{clark1986}:

@@

Similarly, the unit vectors $\mathbf{v}_{1}$, $\mathbf{v}_{2}$, and $\mathbf{v}_{3}$
for prolate ellipsoids (i.e., $a > b = c$) are calculated
by using Eqs. \ref{eq:v1_triaxial_prolate}, \ref{eq:v2_triaxial_prolate}, and
\ref{eq:v3_triaxial_prolate}, but with $\gamma = 0^{\circ}$
\citep{emerson1985}.

@@

for oblate ellipsoids (i.e., $a < b = c$) are calculated as follows:

@@

These formulas are similar to those presented by \citep{emerson1985}.

>>>>

For triaxial ellipsoids (i.e., $a > b > c$) and prolate ellipsoids
(i.e., $a > b = c$), these unit vectors may be given by \citep{clark1986}:

@@

\citet{emerson1985} also calculate the unit vectors $\mathbf{v}_{1}$, $\mathbf{v}_{2}$,
and $\mathbf{v}_{3}$ by using Eqs. \ref{eq:v1_triaxial_prolate},
\ref{eq:v2_triaxial_prolate}, and \ref{eq:v3_triaxial_prolate}, but
with $\gamma = 0^{\circ}$.

@@

for oblate ellipsoids (i.e., $a < b = c$) may be calculated as follows:

@@
